---
title: "Differential Methylation Regions on Genome of Gastric Cancer"
author: "bioinformatic group@AMS"
date: "June 13,2019"
output: 
  pdf_document: 
    latex_engine: xelatex

---

```{r setup, include=FALSE,echo=F}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(data.table)
library(sqldf)
library(umap)
library(kableExtra)
library(tidyr)

```

## Datasets used in this study
 Only two samples match gastric cancer in the methylation dataset of TCGA (The Cancer Genome Atlas), this requires us to look for more other datasets.
 After searching the GEO repository of NCBI , we found the following 4 studies focus on the methylation status of gastric cancer genome.


```{r sampleTable,echo=F,results='asis'}
 
df1 <- data.frame('access'=c('GSE30601','GSE25869','GSE99553','GSE103186'),
                  'platform'=c('GPL8490','GPL8490','GPL13534','GPL13534'),
                 'normalNumber'=c(94,32,84,61),'cancerNumber'=c(203,32,0,130),
                 'reference'=1:4)
   
kable(df1,"latex", booktabs = T) %>%
  kable_styling(latex_options = c("striped"),full_width = T)
```

## Differential methylation regions of gastric cancer 

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
